---
title: "Figure 1 GH Comments"
author: "jcbioinformatics"
date: "2026-05-12"
output:
  html_document:
    toc: true
    toc_float: true  
params: 
  comments_counts: "21,5"
  comments_labels: "First,Second"
  prs_omit: "8680,8801"
  input_path: "./prs_merged_comments.txt"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Overview

Create figure showing number of comments for merged nf-core/modules PRs

Text file with counts should be generated with: `gh pr list --state merged --json number,title,comments --template '{{range .}}{{.number}}: {{.title}} ({{len .comments}} comments){{"\n"}}{{end}}' --limit 12000 > prs_merged_comments.txt`
- Move into cloned repository prior to running that command
- `gh` can be installed with conda (version 2.92.0 used). 

## Parameters

Describe each parameter

* Paths
  + `input_path`: File containing PR information as generated with `gh pr list --state merged --json number,title,comments --template '{{range .}}{{.number}}: {{.title}} ({{len .comments}} comments){{"\n"}}{{end}}'`

* Processing
  + `comments_counts`: Comma delimited list of comment counts for PRs of interest
  + `comments_labels`: Comma delimited list of identifiers to use for PRs of interest
  + `prs_omit`: Comma delimited list of PR ids to omit

## Other Notes

Comment count does NOT necessarily equal number given for Conversation on the web since the counts in this case do NOT include replies or code review comments



```{r set Rmd version}

# Follow semantic versioning as described at:
# https://semver.org/

rmd_version <- "v1.0.0"


```


# Parameters

```{r show parameters}

for (par in names(params)){
  print(
    paste(
      par,
      params[[par]],
      sep = ": "
    )
  )
}


```


# Processing

```{r load libraries}

library(ggrepel)
library(tidyverse)


```


```{r set parameters}

comments_counts <- strsplit(params$comments_counts, split = ",")[[1]]
comments_labels <- strsplit(params$comments_labels, split = ",")[[1]]
prs_omit <- strsplit(params$prs_omit, split = ",")[[1]]
input_path <- params$input_path


```


```{r parse data}

pr_comments_df <- read.table(
  input_path,
  sep = "\t",
  quote = "",
  comment.char = "",
  col.names = c("Data")
)

pr_comments_df_formatted <- pr_comments_df %>% 
  mutate(
    ID = gsub(":.*", "", Data),
    Comments = gsub(
      ".*\\(([0-9]+) comments\\)$", "\\1", Data
    ),
    Comments = as.numeric(Comments),
    X_plot = "Comments"
  ) %>% 
  filter(
    !ID %in% prs_omit
  )

my_comments_df <- data.frame(
  Label = comments_labels,
  Comments = comments_counts,
  X_plot = "Comments"
) %>% 
  mutate(
    Comments = as.numeric(Comments)
  )

```


```{r make plot}

boxplot_comments <- pr_comments_df_formatted %>% 
  ggplot(
    aes(x = X_plot, y=Comments)
  ) +
  geom_boxplot(
    fill="#24B064",
    color="black",
    alpha=0.8
  ) +
  theme_bw() +
  theme(
    axis.text = element_text(size = 18),
    axis.text.x = element_blank(),
    axis.title = element_text(size = 24)
  ) +
  geom_point(
    data = my_comments_df,
    color = "forestgreen",
    size = 4
  ) +
  geom_text_repel(
    data = my_comments_df,
    nudge_x = 0.03,
    aes(
      label = Label
    ),
    size = 6,
    color = "darkgreen"
  ) +
  xlab("") +
  ylab("Comments Count") 


```


# Results

```{r show plot, dpi=300, fig.width=4, fig.height=5}

boxplot_comments


```


# Versions

```{r show versions}

sessionInfo()


```


```{r show Rmd version}

print(
  paste(
    knitr::current_input(),
    "version:",
    rmd_version
  )
)

print(
  paste(
    "Executed:", Sys.time()
  )
)


```
